### 2018-05-28 Paper/disc.tex
..

In this work, we have presented a systematic approach for constructing a reduced-order
surrogate for scientific and engineering applications. Dimension reduction is accomplished
by identifying uncertain parameters that contribute relatively less towards the uncertainty
in the quantity of interest. These parameters deemed as \textit{unimportant} are determined
using a screening metric, defined in~\eqref{eq:cmu}. Initially, the metric is estimated
using model evaluations at a small set of samples in the parameter domain. However, these
estimates are refined by subsequent enrichment of the sample set during the screening
procedure presented in Algorithm~\ref{alg:screen}. The outcome of parameter screening is
assessed for the scope of dimension reduction. In a favourable scenario, a reduced-order
surrogate (ROS) is constructed. The ROS is tested for accuracy in a least-squares sense
as well as a probabilistic sense using a validation test suite. In the proposed framework,
a surrogate in the full-space (FSS) is constructed in tandem with parameter screening using
the available set of model evaluations. Both, ROS and FSS are
constructed using regression-based sparse basis methods. Simultaneous construction
of the FSS ensures that the computational effort associated with the proposed framework
does not overshoot the effort required to construct the FSS directly.
Hence, the ROS is constructed only in situations where computational gains are
expected.

@@

Based on the results presented for a variety of test problems, 
and a higher-dimensional chemical kinetics application in this work, it can be said that the
proposed framework seems quite promising in its potential for identifying favourable
scenarios for constructing a reduced-order surrogate in a computationally efficient manner. 
However, it is important to remain cognizant about the underlying limitations of the
framework. For instance, it does not account for the existence of possible correlation 
between the uncertain parameters of the model, although in many cases, correlations
between parameters are not well understood, and assuming mutual independence 
would be reasonable. Similarly, the quantity of interest is required to be differentiable
with respect to each parameter in the considered domain. This condition, however, must
anyways be satisfied for the resulting surrogate to be able to represent the input-output
relationship for a given model with reasonable accuracy. Finally, careful assessment 
and decision-making is required with regards to proceeding with the
construction of a reduced-order surrogate based on the outcome of parameter
screening, and accuracy of the most-recent full-space surrogate as well as 
allocation of computational resources for parameter screening, and constructing the
validation test suite. Implementation to more advanced
applications in the future would enable further development of the proposed framework.

>>>>

In this work, we have presented a systematic approach for constructing a reduced-order
surrogate for scientific and engineering applications. Dimension reduction is accomplished
by identifying uncertain parameters that contribute relatively less towards the uncertainty
in the quantity of interest. These parameters deemed as \textit{unimportant} are determined
using a screening metric, defined in~\eqref{eq:cmu}. Initially, the metric is estimated
using model evaluations at a small set of samples in the parameter domain. However, these
estimates are refined by subsequent enrichment of the sample set during the screening
procedure presented in Algorithm~\ref{alg:screen}. The outcome of parameter screening is
assessed for the scope of dimension reduction. In a favorable scenario, a reduced-order
surrogate (ROS) is constructed. The ROS is tested for accuracy in a least-squares sense
as well as a probabilistic sense using a validation test suite. In the proposed framework,
a surrogate in the full-space (FSS) is constructed in tandem with parameter screening using
the available set of model evaluations. Both, ROS and FSS are
constructed using regression-based sparse basis methods. Simultaneous construction
of the FSS ensures that the computational effort associated with the proposed framework
does not overshoot the effort required to construct the FSS directly.
Hence, the ROS is constructed only in situations where computational gains are
expected.

@@

Based on the results presented for a variety of test problems, 
and a higher-dimensional chemical kinetics application in this work, it can be said that the
proposed framework seems quite promising in its potential for identifying favorable
scenarios for constructing a reduced-order surrogate in a computationally efficient manner. 
However, it is important to remain cognizant about the underlying limitations of the
framework. For instance, it does not account for the existence of possible correlation 
between the uncertain parameters of the model, although in many cases, correlations
between parameters are not well understood, and assuming mutual independence 
would be reasonable. Similarly, the quantity of interest is required to be differentiable
with respect to each parameter in the considered domain. This condition, however, must
anyways be satisfied for the resulting surrogate to be able to represent the input-output
relationship for a given model with reasonable accuracy. Finally, careful assessment 
and decision-making is required with regards to proceeding with the
construction of a reduced-order surrogate based on the outcome of parameter
screening, and accuracy of the most-recent full-space surrogate as well as 
allocation of computational resources for parameter screening, and constructing the
validation test suite. Implementation to more advanced
applications in the future would enable further development of the proposed framework.
